### 2021-04-01 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Extension of Michelson/Introduction chapter 4

>>>>

\chapter{List accessing in Michelson}\label{apx:nth}

\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=,
				 label=lst:nth_liq,
				 caption=Possible implementation of \texttt{nth} in Liquidity]{listings/nth.liq}

\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=,
				 label=lst:nth_tz,
				 caption=\lstref{lst:nth_liq} compiled to Michelson]{listings/nth.tz}
